Text Is All You Need

### 2023-05-11 docs/hes_final/presentation.qmd
Push more to notes

:::{.notes}
We explored the possibility of predicting future geopolitical conflict escalation using a global collection of news publications
:::
---

- The neural network-based models appear to generalize better across geographies while the statistical model provided a size/cost of deployment advantage.
- While this work did not produce a single best model for conflict escalation predictions, it demonstrated the possibility of such predictions from primarily text data. 
- We described several approaches for data aggregation and modeling. We hope this work will contribute to both UNICEF operations and political science research. 
- The performance results can serve as a benchmark for future research projects in this field.

>>>>

:::{.notes}
- We explored the possibility of predicting future geopolitical conflict escalation using a global collection of news publications
- The neural network-based models appear to generalize better across geographies while the statistical model provided a size/cost of deployment advantage.
- While this work did not produce a single best model for conflict escalation predictions, it demonstrated the possibility of such predictions from primarily text data. 
- We described several approaches for data aggregation and modeling. We hope this work will contribute to both UNICEF operations and political science research. 
- The performance results can serve as a benchmark for future research projects in this field.
:::
